---
title: "Getting started with icon"
author: "Mitchell O'Hara-Wild"
date: "2018-04-03"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting started with icon}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
library(icon)
```

## Using an icon

The icon package makes it easy to embed popular web-font icons in rmarkdown documents.

Icons can be added using inline code `icon::fa("rocket")` (`r icon::fa("rocket")`) and chunks:

```{r}
icon::fa("rocket")
```

In this case, the icon being used is the 'rocket' icon from [Font Awesome](https://fontawesome.com/) (`fa-rocket`). The font library is specified using the function name, and the specific icon is provided as the first argument. 

Icon specific functions are also available which makes it easier to tab-complete icon names:

```{r}
icon::fa_rocket()
```


## Finding the right icon

The names of available [Font Awesome](https://fontawesome.com/) icons can be found using `icon::fa_iconList`, or by looking on the Font Awesome [icon list](https://fontawesome.com/v4.7.0/icons/).

The package also supports icons from [academicons](http://jpswalsh.github.io/academicons/) (`icon::ai()`: `r icon::ai()`) and [ionicons](http://ionicons.com/) (`icon::ii()`: `r icon::ii()`).

## Customising the icon

The customisation options available with Font Awesome icons (as shown in these [examples](https://fontawesome.com/v4.7.0/examples/)) are supported for all icon libraries using the function arguments.

* Size `icon::fa_rocket(size = 2)`: `r icon::fa_rocket(size = 2)`
* Rotation `icon::fa_rocket(rotate = 180)`: `r icon::fa_rocket(rotate = 180)`
* Flip `icon::fa_rocket(flip = "horizontal")`: `r icon::fa_rocket(flip = "horizontal")`
* Animation `icon::fa_rocket(animate = "spin")`: `r icon::fa_rocket(animate = "spin")`
* Fixed width `icon::fa_rocket(fixed_width = TRUE)`: `r icon::fa_rocket(fixed_width = TRUE)`
* Border `icon::fa_rocket(border = TRUE)`: `r icon::fa_rocket(border = TRUE)`
* Pull `icon::fa_rocket(pull = "left")`: `r icon::fa_rocket(pull = "left")`

## Acknowledgements

The icon package would not be possible without the generous availability of public web-font icon libraries:

* [Font Awesome](http://fontawesome.io) `r fa()`

* [Academicons](http://jpswalsh.github.io/academicons/) `r ai()`

* [Ionicons](http://ionicons.com) `r ii()`

This project was created during the [rOpenSci OzUnconf 2017](http://ozunconf17.ropensci.org). Thanks `r fa_r_project()`!
